---
title: "Documentation for My Shiny App"
subtitle: "A Shiny app which can predict diamond price by carat"
author: "Yunyi Zhang"
date: "April 13, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

A diamond price is highly related to its carat, so I have developed a prediction model to predict a diamond's price based on its carat. The following is a sample of the diamond price and carat data:
```{r}
library(ggplot2)
head(diamonds[,c('carat', 'price')])
```

## Prediction Model

The prediction model used the diamond dataset included in the ggplot2 library. The following code is used to get the prediction model:
```{r, echo=TRUE}
library(ggplot2)
model <- lm(price~carat, data=diamonds)
summary(model)
```

## Embed the Prediction Model to Shiny App

I developed a Shiny App, which can let the user input the carat through a slide bar, and then the app will automatically show the price through a black point on a graph. The following is an example of the graph:
```{r}
    data_on_plot <- data.frame(carat = seq(from=0.1, to=20, by=0.1))
    data_on_plot$price <- predict(model, newdata = data_on_plot)
    rownames(data_on_plot) = seq(from=0.1, to=20, by=0.1)
    point <-  data_on_plot['12',]
    ggplot(data=data_on_plot, aes(x=carat, y=price)) + 
      geom_line() + 
      geom_point(data=point, size=5, mapping = aes(x=carat, y=price))
```



## Reference

For more information about the diamond dataset, please refer to:

https://www.rdocumentation.org/packages/UsingR/versions/2.0-5/topics/diamond

Source code of ui.R and server.R of the Shiny App can be found at:

<a href="https://github.com/zhangyyz/DevelopingDataProductsWeek4PeerReview" target="_blank">https://github.com/zhangyyz/DevelopingDataProductsWeek4PeerReview</a>




